Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-10-24 doc/prelim/presentation/prelim_presentation.tex
adding projection methods to presentation

  We choose a search subspace $\mathcal{K}$ and a search subspace
  $\mathcal{L}$ and determine the solution to the linear problem by
  extracting the solution from the search subspace:
  \[
  \tilde{\ve{x}} = \ve{x}_0 +
  \boldsymbol{\delta},\ \boldsymbol{\delta} \in \mathcal{K}\:,
  \]
  and by constraining it with the constraint subspace:
  \[
  \langle \tilde{\ve{r}},\ve{w} \rangle = 0,\ \forall \ve{w} \in
  \mathcal{L}\:.
  \]

>>>>

  We choose a \textit{search subspace} $\mathcal{K}$ and a
  \textit{constraint subspace} $\mathcal{L}$ and determine the solution
  to the linear problem by extracting the solution from the search
  subspace:
  \[
  \tilde{\ve{x}} = \ve{x}_0 +
  \boldsymbol{\delta},\ \boldsymbol{\delta} \in \mathcal{K}\:,
  \]
  and by constraining it with the constraint subspace:
  \[
  \langle \tilde{\ve{r}},\ve{w} \rangle = 0,\ \forall \ve{w} \in
  \mathcal{L}\:.
  \]

  We can generate a more physical and geometric-based understanding of
  these constraints by writing the new residual as:
  \[
  \tilde{\ve{r}} = \ve{r}_0 - \ve{A}\boldsymbol{\delta}
  \]

  If $\tilde{\ve{r}}$ is to be orthogonal to $\mathcal{L}$, then
  $\ve{A}\boldsymbol{\delta}$ must be the projection of $\ve{r}_0$
  onto the subspace $\mathcal{L}$ that eliminates the components of
  the residual that exist in $\mathcal{L}$.

%%---------------------------------------------------------------------------%%
\begin{frame}{The Orthogonality Constraint}

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{1.25}{
        \input{orthogonal_residual.pdftex_t} }
    \end{center}
    \caption{\textbf{Orthogonality constraint of the new residual with
        respect to $\mathcal{L}$.} \textit{By projecting $\ve{r}_0$ onto
        the constraint subspace, we minimize the new residual by
        removing those components.}}
    \label{fig:linear_projection_constraint}
  \end{figure}

  From this we note:
  \[
  ||\tilde{\ve{r}}||_2 \leq ||\ve{r}_0||_2,\ \forall \ve{r}_0 \in
  \mathbb{R}^N\:,
  \]
  meaning that the residual of the system will always be
  \textit{minimized} with respect to the constraints.

%%---------------------------------------------------------------------------%%
\begin{frame}{Projection Iteration}

  Consider a matrix $\ve{V}$ to form a basis of $\mathcal{K}$ and a
  matrix $\ve{W}$ to form a basis of $\mathcal{L}$.

  \[
  \boldsymbol{\delta} = \ve{V}\ve{y},\ \forall \ve{y} \in
  \mathbb{R}^N\:.
  \]

  From the orthogonality constraint it then follows that:
  \[
  \ve{y} = (\ve{W}^T\ve{A}\ve{V})^{-1}\ve{W}^T\ve{r}_0\:,
  \]

  We can then form an iteration sequence:
  \[
  \ve{r}^k = \ve{b} - \ve{A}\ve{x}^k
  \]
  \[
  \ve{y}^k = (\ve{W}^T\ve{A}\ve{V})^{-1}\ve{W}^T\ve{r}^k
  \]
  \[
  \ve{x}^{k+1} = \ve{x}^k + \ve{V}\ve{y}^k\:,
  \]

  with $\ve{V}$ and $\ve{W}$ updated prior to each iteration.

%%---------------------------------------------------------------------------%%
\begin{frame}{Krylov Subspace Methods}

%%---------------------------------------------------------------------------%%
\begin{frame}{GMRES}
